Finding ARG1 of Partitive Nouns in NomBank with DistilBERT

### 2022-05-03 src/paper.tex
Update

\author{Ziyang Zeng \\
  Dept. of Computer Science \\
  New York University \\
  \texttt{zz2960@nyu.edu}}

@@

BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks. BERT came a decade later than the release of NomBank and there's been little previous work in using it to conduct NomBank-based tasks and related experiments. However, as powerful as BERT is, its large parameters size makes it significantly more computationally expensive to train and use. On the other hand, DistilBERT is a distilled student model of BERT that retains 97\% of BERT's language understanding capabilities while being 40\% smaller and 60\% faster.

@@

NomBank (Meyers et al., 2004c), as a databank extending the frames of NOMLEX and PropBank, annotates argument structures of common nouns similar to how PropBank annotates predicating verbs. The development of the NomBank corpus has supported the work of (Jiang and Ng, 2006) and (Liu and Ng, 2007). Each study tested the hypothesis that machine learning methodologies and representations used in verbal SRL (cf. (Pradhan et al., 2005)) can be ported to the task of NomBank SRL. (Liu and Ng, 2007) reports an overall f-measure score of 0.7283 using automatically generated parse trees, demonstrating that modest performance can be achieved using basic approaches developed in the verbal domain. Both studies also investigated the use of features specific to the task of nominal SRL, but observed only marginal performance gains.

>>>>

\author{Ziyang Zeng \\
  Dept. of Computer Science \\
  New York University \\
  251 Mercer Street, New York, NY \\
  \texttt{zz2960@nyu.edu}}

@@

BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks. BERT came a decade later than the release of NomBank and there's been little previous work using it to conduct NomBank-based tasks and related experiments. However, as powerful as BERT is, its large parameters size makes it significantly more computationally expensive to train and use. On the other hand, DistilBERT is a distilled student model of BERT that retains 97\% of BERT's language understanding capabilities while being 40\% smaller and 60\% faster. This makes it a great candidate to train when facing with limited resources.

@@

NomBank (Meyers et al., 2004c), as a databank extending the frames of NOMLEX and PropBank, annotates argument structures of common nouns similar to how PropBank annotates predicating verbs. The development of the NomBank corpus has made several other work on argument structure extraction more accessible. Jiang and Ng (2006) attempts the first NomBank-based automatic semantic role labeling system after the databank's release. Ping (2006)  adapts a PropBank-based SRL system to the SRL task of NomBank, achieving an overall F1 score of 72.73 on section 23 of the NomBank corpus.

More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based langauge models. The latest development on this is transformers-based models including BERT. BERT, or Bidirectional Encoder Representations from Transformers (Devlin et al., 2018), is a pretrained language model that can achieve state-of-the-art results on a variety of natural language processing tasks.
